### 2017-08-15 architecture.tex
a few typos

Apollo, an analyst, authenticates to \NAME and requests access to a private safe collection.
The request is added to the stewarship dashboard and is visible to all stewards
of that collection. Daphnie, a steward for the requested
safe collection views and then approves Apollo's request for a period of $n$ days.
The approval process adds the appropriate policies to the
safe collection granting access to Apollo. Apollo can now submit analysis tasks through the various
interfaces offered by \NAME, that specify data items from the safe collection as inputs.
The REST API marks the analysis task as export controlled since it draws results
from an export controlled safe collection.
The submitted task is posted to an internal queue from which a
worker node in the \NAME private subnet picks up Apollo's task. The worker node assumes Apollo's identity and, with
his credentials, requests data from the safe collection. Since Apollo now has read privileges for the
safe collection, the data is fetched to the worker node on which the analysis task is executed.
Upon completion, the worker node puts the generated results in the export-controlled
output directory of the safe collection since these results are generated from export controlled data.
Apollo's analysis is now complete, but he is unable to view the
results as they require steward approval. This flow is show in \figurename~\ref{fig:flow1}

@@

Safe collection policies are expressed on \NAME's managed
data via AWS Identity and Access Management (IAM) policies
and S3 bucket policies.
A safe collection is described in CloudFormation templates, where
CloudFormation provides a reproducible method for instantiating infrastructure
based on a standard JSON description. For example, it defines
the S3 bucket, bucket policies granting exclusive administrative privileges to a steward role,
and IAM policies granting appropriate privileges to \NAME worker machines to store analysis results.
%This allows safe-collection descriptions to be verifiable, reproducible, and shareable.

To enable the definition and management of safe collection policies we
rely on a meta-policy model. The meta-policy model enables the specification
of the policies described above. Each safe collection is associated with a steward
(or group of stewards) who manage the collection's policies. To simplify use, the meta-policy schema
is translated to a web-based form that can be completed by administrators during the creation of a safe collection.
The defined policies (from the form or otherwise) are stored as a set of secure tags
on the collection's data storage bucket. The schema is enforced by the various services that interact
with the safe collection. The schema and the generated form are shown in \figurename~\ref{fig:schema}

>>>>

Apollo, an analyst, authenticates to \NAME and requests access to a private safe collection.
The request is added to the stewarship dashboard and is visible to all stewards
of that collection. Daphnie, a steward for the requested
safe collection views and then approves Apollo's request for a period of $n$ days.
The approval process adds the appropriate policies to the
safe collection granting access to Apollo. Apollo can now submit analysis tasks through the various
interfaces offered by \NAMENS, that specify data items from the safe collection as inputs.
The REST API marks the analysis task as export controlled since it draws results
from an export controlled safe collection.
The submitted task is posted to an internal queue from which a
worker node in the \NAME private subnet picks up Apollo's task. The worker node assumes Apollo's identity and, with
his credentials, requests data from the safe collection. Since Apollo now has read privileges for the
safe collection, the data is fetched to the worker node on which the analysis task is executed.
Upon completion, the worker node puts the generated results in the export-controlled
output directory of the safe collection since these results are generated from export controlled data.
Apollo's analysis is now complete, but he is unable to view the
results as they require steward approval. This flow is show in \figurename~\ref{fig:flow1}

@@

Safe collection policies are expressed on \NAMENS's managed
data via AWS Identity and Access Management (IAM) policies
and S3 bucket policies.
A safe collection is described in CloudFormation templates, where
CloudFormation provides a reproducible method for instantiating infrastructure
based on a standard JSON description. For example, it defines
the S3 bucket, bucket policies granting exclusive administrative privileges to a steward role,
and IAM policies granting appropriate privileges to \NAME worker machines to store analysis results.
%This allows safe-collection descriptions to be verifiable, reproducible, and shareable.

To enable the definition and management of safe collection policies we
rely on a meta-policy model. The meta-policy model enables the specification
of the policies described above. Each safe collection is associated with a steward
(or group of stewards) who manage the collection's policies. To simplify use, the meta-policy schema
is translated to a web-based form that can be completed by administrators during the creation of a safe collection.
The defined policies (from the form or otherwise) are stored as a set of secure tags
on the collection's data storage bucket. The schema is enforced by the various services that interact
with the safe collection. The schema and the generated form are shown in \figurename~\ref{fig:schema}.

### 2017-08-15 relatedwork.tex
Removing comment from kyle. ICPSR says they have two enclaves here: https://www.icpsr.umich.edu/icpsrweb/content/ICPSR/access/restricted/enclave.html
a few typos

Secure data enclaves have a long and varied history starting with air gapped systems that are physically
disconnected from the internet.
While there are many examples of data enclaves, to the best of our knowledge none provide 
the stewardship and policy-based models used in \NAME. In this sections, we briefly review a range of data enclaves.

@@

The ICPSR data enclave \cite{icpsr} hosts sensitive datasets
for social science research. While the majority of the datasets are public, ICPSR
also manages restricted use datasets such as crime
data that are protected in data enclaves. They offer two types of data enclave: physical
and virtual. \kyle{Yadu - is this true?} The physical data enclave is a single protected server that is disconnected
from the internet and is accessible only in person. The virtual enclave is a remote desktop solution that is designed
to prevent copying of data. Systems such as these offer security at the cost of accessibility and ease of use while, at
the same time, lacking a solution to the fundamental problem of users manually copying sensitive microdata records.

@@

The NCI Genomic Data Commons \cite{grossman2016toward} hosts several Petabytes of
genomic data, and provides an on-premise cloud model to enable computation on these sensitive datasets.
While the on-premise infrastructure meets compliance requirements, this choice leads to added costs associated with
building and maintaining production compute infrastructure---an approach that is unlikely to be 
broadly available to a wide range of scientists. \NAME, and other cloud-based enclaves, benefit
significantly from the low-cost cloud resources made possible due to providers' economies of scale.

>>>>

Secure data enclaves have a long and varied history starting with air gapped systems that are physically
disconnected from the internet.
While there are many examples of data enclaves, to the best of our knowledge none provide 
the stewardship and policy-based models used in \NAMENS. In this sections, we briefly review a range of data enclaves.

@@

The ICPSR data enclave \cite{icpsr} hosts sensitive datasets
for social science research. While the majority of the datasets are public, ICPSR
also manages restricted use datasets such as crime
data that are protected in data enclaves. They offer two types of data enclave: physical
and virtual. The physical data enclave is a single protected server that is disconnected
from the internet and is accessible only in person. The virtual enclave is a remote desktop solution that is designed
to prevent copying of data. Systems such as these offer security at the cost of accessibility and ease of use while, at
the same time, lacking a solution to the fundamental problem of users manually copying sensitive microdata records.

@@

The NCI Genomic Data Commons \cite{grossman2016toward} hosts several Petabytes of
genomic data, and provides an on-premise cloud model to enable computation on these sensitive datasets.
While the on-premise infrastructure meets compliance requirements, this choice leads to added costs associated with
building and maintaining production compute infrastructure---an approach that is unlikely to be 
broadly available to a wide range of scientists. \NAMENS, and other cloud-based enclaves, benefit
significantly from the low-cost cloud resources made possible due to providers' economies of scale.
